Modeling Galaxy Spectral Energy Distributions in the SDSS Spectroscopic Survey

### 2002-02-10 docs/paper/paper.tex
fixed stuff
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@29 75dff457-8751-0410-ab1a-cd701654ce6b

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.
\begin{abstract}
Certain astronomical questions, such as the evolution of the
luminosity function of galaxies and the relationship between galaxy
luminosities and galaxy colors, require transforming inherently
redshift-dependent measurements of galaxy magnitudes into measures of
galaxy properties which are consistent over a range of redshifts.  As
part of the task of addressing these questions, which we will
investigate in subsequent papers, we implement here the method of
\citet{csabai00a} for fitting spectral energy distributions (SEDs) to
broad-band photometric observations, in the context of the optical
observations of the Sloan Digital Sky Survey (SDSS). Linear
combinations of four spectral templates can reproduce the five SDSS
magnitudes of galaxies to the precision of the photometry. Expressed
in the correct coordinate system, the distribution of the coefficients
of the templates is planar, and in fact nearly linear. The resulting
reconstructed SEDs (the sum of the templates) can be used to recover
fixed-frame magnitudes over a range of redshifts. We show that the
results of doing so yield consistent results within the SDSS Main
Galaxy Sample and the SDSS Luminous Red Galaxy Sample, in the sense
that within each sample the trend with redshift of intrinsic colors
for similar type galaxies are small. A potential problem in the
measurement of the SDSS filter response curves is noted. We also
validate the results using galaxy spectrophotometry.  All code and
templates from this paper are publicly available and well-documented;
they are designed such that they can easily be incorporated into other
applications. The code is easily adapted to handle galaxy observations
in any AB magnitude system in the rest-frame optical regime.
\end{abstract}

>>>>

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.
\begin{abstract}
Certain astronomical questions, such as the evolution of the
luminosity function of galaxies and the relationship between galaxy
luminosities and galaxy colors, require transforming inherently
redshift-dependent measurements of galaxy magnitudes into measures of
galaxy properties which are consistent over a range of redshifts.  To
address these astronomical questions, investigated in detail in
subsequent papers, we implement here the method of \citet{csabai00a}
for fitting spectral energy distributions (SEDs) to broad-band
photometric observations, in the context of the optical observations
of the Sloan Digital Sky Survey (SDSS). Linear combinations of four
spectral templates can reproduce the five SDSS magnitudes of galaxies
to the precision of the photometry. Expressed in the correct
coordinate system, the distribution of the coefficients of the
templates is planar, and in fact nearly linear. The resulting
reconstructed SEDs (the sum of the templates) can be used to recover
fixed-frame magnitudes over a range of redshifts. We show that the
results of doing so yield consistent results within the SDSS Main
Galaxy Sample and the SDSS Luminous Red Galaxy Sample, in the sense
that within each sample the trend with redshift of intrinsic colors
for similar type galaxies are small. A potential problem in the
measurement of the SDSS filter response curves is noted. We also
validate the results using galaxy spectrophotometry.  All code and
templates from this paper are publicly available and well-documented;
they are designed such that they can easily be incorporated into other
applications. The code is easily adapted to handle galaxy observations
in any AB magnitude system in the rest-frame optical regime.
\end{abstract}
